### 2018-10-28 Sections/economics_of_the_quantum_internet.tex
Added static computational return

%
% Per qubit computational power
%

\section{Per qubit computational power}\label{sec:NPSF}\index{Per qubit computational power}

\dropcap{O}{ne} parameter that appears ubiquitously in the upcoming economic models and warrants a definition of its own is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{per qubit computational power},

\begin{definition}[Per qubit computational power]\label{def:NPSF}\index{Per qubit computational power}
The per qubit computational power is defined as the computational power per qubit,
\begin{align}
\chi_\mathrm{sc}(n) = \frac{f_\mathrm{sc}(n)}{n}.
\end{align}
\end{definition}

@@

\begin{figure}[htb!]\index{Per qubit computational power}
	\includegraphics[clip=true, width=0.475\textwidth]{network_price_scaling_factor}
	\captionspacefig \caption{Per qubit computational power, $\chi_\mathrm{sc}$, as a function of several representative computational scaling functions, $f_\mathrm{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

@@

This clearly implies that as the global quantum network expands over time, so too does the computational payback on investment into network expansion, or equivalently, the cost per unit of additional classical-equivalent processing time decreases exponentially.

@@

@@

	\begin{flushleft}Per qubit computational power (Sec.~\ref{sec:NPSF})\end{flushleft} & \[\chi_\mathrm{sc}(n)=\frac{f_\mathrm{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\

@@

>>>>

%
% Per-qubit computational power
%

\section{Per-qubit computational power}\label{sec:NPSF}\index{Per-qubit computational power}

\dropcap{O}{ne} parameter that appears ubiquitously in the upcoming economic models and warrants a definition of its own is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{per-qubit computational power},

\begin{definition}[Per-qubit computational power]\label{def:NPSF}\index{Per-qubit computational power}
The per-qubit computational power is defined as the computational power per qubit,
\begin{align}
\chi_\mathrm{sc}(n) = \frac{f_\mathrm{sc}(n)}{n}.
\end{align}
\end{definition}

@@

\begin{figure}[htb!]\index{Per-qubit computational power}
	\includegraphics[clip=true, width=0.475\textwidth]{network_price_scaling_factor}
	\captionspacefig \caption{Per-qubit computational power, $\chi_\mathrm{sc}$, as a function of several representative computational scaling functions, $f_\mathrm{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

@@

@@

%
% Static Computational Return
%

\section{Static computational return}\index{Static computational return}\label{sec:static_comp_ret}

\dropcap{T}{he} computational leverage phenomena clearly implies that as the global quantum network expands over time, so too does the computational payback on investment into network expansion, or equivalently, the cost per unit of additional classical-equivalent processing time decreases exponentially.

To formalise this, consider the case where a user purchases an initial single qubit \mbox{$n_\mathrm{user}=1$}, while the global network expands over time as \mbox{$n_\mathrm{global}=N_t$}. Then the classical-equivalent computational power of the user is,

\begin{definition}[Static computational return]\index{Static computational return} The static (i.e fixed-investment) computational return is the classical-equivalent processing power of a user's time-share, where the user has a fixed investment of one qubit, whereas the network is allowed to expand over time arbitrarily,
\begin{align}
	r_\mathrm{static}(t) &= \frac{f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= \chi_\mathrm{sc}(N_t),
\end{align}
which is equivalent to the collective per-qubit computational power of the entire network.
\end{definition}

Examples for this relationship are equivalent to those presented earlier in Fig.~\ref{fig:NPSF}.

@@

	\begin{flushleft}Per-qubit computational power (Sec.~\ref{sec:NPSF})\end{flushleft} & \[\chi_\mathrm{sc}(n)=\frac{f_\mathrm{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\

@@

	\begin{flushleft}Static computational return (Sec.~\ref{sec:static_comp_ret})\end{flushleft} & \[r_\mathrm{static}(t) = \frac{f_\mathrm{sc}(N_t)}{N_t}\] & \[1\] & \[{N_t}^{p-1}\] & \[\frac{e^{N_t}}{N_t}\] \\
